\chapter{Project Risks and Conclusions}

The project was divided up into several modules as was outlined in the approach and preliminary design section. The current status and our feelings on the ability to complete these modules is outlined below.

\begin{description}
\item[Drive by wire] For this system we have already completed a fairly detailed preliminary design on how the system will work and the different sections will communicate and have begun ordering the required parts. We are all fairly confident that we will have this section completed well within the allotted time for the project

\item[Sensor interfacing] While there are no concrete plans for this module as of right now the group has began to research which sensors would best suit the application and are within our budget. The group has also looked into the best way to interface them with the control system. Again we are fairly confident that this section can be completed in the time allowed

\item[High level control of systems] For this section we do not yet have detailed plans as to the development of the functions however we have brainstormed what many of the functions will be and what sensors they will require. We believe that as long as no unforeseen problems occur during earlier parts that this is again achievable.

\item[Simple autonomous behaviour] Apart from the idea of what we wish the kart to do and a rough idea of some of the programming that would be involved no work has been done on this section. We currently believe that if all other sections are problem free and go smoothly that we may have time to finish a functional but buggy version of this behaviour. We do not feel however we will have time to get this system working 100\%

\item[Complex autonomous behaviour] We believe that getting the vehicle to a point where this part is operational is a total pipe dream. It is our goal this year to develop the system to the point where groups in future years will be able to start at this point allowing them more time to develop the highly complex algorithms this will require. If time allows we will begin on this section however currently this appears unlikely.
\end{description}